FictionEro-2 - Data Cleaning

### 2025-08-05 study2/analysis/1_cleaning.qmd
updated data and html cleaning

```{r}
df<- filter(df, !Gender=="Other")
df <- filter(df, !Participant %in% outliers$arousal)
dftask <- filter(dftask, !Participant %in% outliers$arousal)
```

>>>>

Only `r sum(df$SexualOrientation == "Other")` participants self-reported as not being heterosexual, homosexual, nor bisexual, hence they were removed from further analysis.

```{r}
df<- filter(df, !Gender=="Other")
df<- filter(df, !SexualOrientation=="Other")

df <- filter(df, !Participant %in% outliers$arousal)
dftask <- filter(dftask, !Participant %in% outliers$arousal)
```
